---
title: "Mini Data-Analysis Deliverable 1"
output: github_document
---

# Welcome to your (maybe) first-ever data analysis project!

And hopefully the first of many. Let's get started:

1.  Install the [`datateachr`](https://github.com/UBC-MDS/datateachr) package by typing the following into your **R terminal**:

<!-- -->

    install.packages("devtools")
    devtools::install_github("UBC-MDS/datateachr")

2.  Load the packages below.

```{r}
library(datateachr)
library(tidyverse)
library(scales)
library(broom)
```

3.  Make a repository in the <https://github.com/stat545ubc-2022> Organization. You will be working with this repository for the entire data analysis project. You can either make it public, or make it private and add the TA's and Lucy as collaborators. A link to help you create a private repository is available on the #collaborative-project Slack channel. 

# Instructions

## For Both Milestones

-   Each milestone is worth 45 points. The number of points allocated to each task will be annotated within each deliverable. Tasks that are more challenging will often be allocated more points.

-   10 points will be allocated to the reproducibility, cleanliness, and coherence of the overall analysis. While the two milestones will be submitted as independent deliverables, the analysis itself is a continuum - think of it as two chapters to a story. Each chapter, or in this case, portion of your analysis, should be easily followed through by someone unfamiliar with the content. [Here](https://swcarpentry.github.io/r-novice-inflammation/06-best-practices-R/) is a good resource for what constitutes "good code". Learning good coding practices early in your career will save you hassle later on!

## For Milestone 1

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-1.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work below --->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to the mini-analysis GitHub repository you made earlier, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 45 points: 43 for your analysis, 1 point for having your Milestone 1 document knit error-free, and 1 point for tagging your release on Github.

# Learning Objectives

By the end of this milestone, you should:

-   Become familiar with your dataset of choosing
-   Select 4 questions that you would like to answer with your data
-   Generate a reproducible and clear report using R Markdown
-   Become familiar with manipulating and summarizing your data in tibbles using `dplyr`, with a research question in mind.

# Task 1: Choose your favorite dataset (10 points)

The `datateachr` package by Hayley Boyce and Jordan Bourak currently composed of 7 semi-tidy datasets for educational purposes. Here is a brief description of each dataset:

-   *apt_buildings*: Acquired courtesy of The City of Toronto's Open Data Portal. It currently has 3455 rows and 37 columns.

-   *building_permits*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 20680 rows and 14 columns.

-   *cancer_sample*: Acquired courtesy of UCI Machine Learning Repository. It currently has 569 rows and 32 columns.

-   *flow_sample*: Acquired courtesy of The Government of Canada's Historical Hydrometric Database. It currently has 218 rows and 7 columns.

-   *parking_meters*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 10032 rows and 22 columns.

-   *steam_games*: Acquired courtesy of Kaggle. It currently has 40833 rows and 21 columns.

-   *vancouver_trees*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 146611 rows and 20 columns.

**Things to keep in mind**

-   We hope that this project will serve as practice for carrying our your own *independent* data analysis. Remember to comment your code, be explicit about what you are doing, and write notes in this markdown document when you feel that context is required. As you advance in the project, prompts and hints to do this will be diminished - it'll be up to you!

-   Before choosing a dataset, you should always keep in mind **your goal**, or in other ways, *what you wish to achieve with this data*. This mini data-analysis project focuses on *data wrangling*, *tidying*, and *visualization*. In short, it's a way for you to get your feet wet with exploring data on your own.

And that is exactly the first thing that you will do!

1.1 Out of the 7 datasets available in the `datateachr` package, choose **4** that appeal to you based on their description. Write your choices below:

**Note**: We encourage you to use the ones in the `datateachr` package, but if you have a dataset that you'd really like to use, you can include it here. But, please check with a member of the teaching team to see whether the dataset is of appropriate complexity. Also, include a **brief** description of the dataset here to help the teaching team understand your data.

<!-------------------------- Start your work below ---------------------------->

1: cancer_sample
2: vancouver trees
3: flows sample
4: steam games

<!----------------------------------------------------------------------------->

1.2 One way to narrowing down your selection is to *explore* the datasets. Use your knowledge of dplyr to find out at least *3* attributes about each of these datasets (an attribute is something such as number of rows, variables, class type...). The goal here is to have an idea of *what the data looks like*.

*Hint:* This is one of those times when you should think about the cleanliness of your analysis. I added a single code chunk for you below, but do you want to use more than one? Would you like to write more comments outside of the code chunk?

<!-------------------------- Start your work below ---------------------------->

```{r}
### EXPLORE HERE ###

#The following commands were used to explore the data sets chosen:
#class(): To investigate the class of the specified object
#glimpse(): Transposes columns to rows so you can see all the columns in the data set
#head(): returns the first rows of the data set
#summary(): overview of different columns, type and distribution
#tibble::view(): shows data in a separate R studio window

# Cancer sample exploration
class(cancer_sample)
glimpse(cancer_sample)
head(cancer_sample)
summary(cancer_sample)
tibble::view(cancer_sample)

# Vancouver trees exploration
class(vancouver_trees)
glimpse(vancouver_trees)
head(vancouver_trees)
summary(vancouver_trees)
tibble::view(vancouver_trees)

# Flow sample exploration
class(flow_sample)
glimpse(flow_sample)
head(flow_sample)
summary(flow_sample)
tibble::view(flow_sample)

# Steam games exploration
class(steam_games)
glimpse(steam_games)
head(steam_games)
summary(steam_games)
tibble::view(steam_games)


```

<!----------------------------------------------------------------------------->

1.3 Now that you've explored the 4 datasets that you were initially most interested in, let's narrow it down to 2. What lead you to choose these 2? Briefly explain your choices below, and feel free to include any code in your explanation.

<!-------------------------- Start your work below ---------------------------->
After exploring the four options, I selected the cancer sample and flow sample to work with. 

Cancer sample.
This data set is the most related to my field of study (biology) and my previous work in undergrad was on cancer. Therefore, I felt particularly compelled to choose this data set. Also, while looking more closely at the columns, there are a lot of numerical values that we can play around with and maybe link between each other.

Flow sample.
This data set looks more diverse as not all of its columns are based on numerical data, some are qualitative values. Also, it could be used to learn more about quality control in processes as opposed to the cancer sample which is more about collecting the observations and interpreting patterns. 
<!----------------------------------------------------------------------------->

1.4 Time for the final decision! Going back to the beginning, it's important to have an *end goal* in mind. For example, if I had chosen the `titanic` dataset for my project, I might've wanted to explore the relationship between survival and other variables. Try to think of 1 research question that you would want to answer with each dataset. Note them down below, and make your final choice based on what seems more interesting to you!

<!-------------------------- Start your work below ---------------------------->
Cancer sample
Is there a relationship between the diagnosis and the mean area in the samples?

Flow sample
Is there a change on the difference between the maximum and minimum values over the years?

<!----------------------------------------------------------------------------->

# Important note

Read Tasks 2 and 3 *fully* before starting to complete either of them. Probably also a good point to grab a coffee to get ready for the fun part!

This project is semi-guided, but meant to be *independent*. For this reason, you will complete tasks 2 and 3 below (under the **START HERE** mark) as if you were writing your own exploratory data analysis report, and this guidance never existed! Feel free to add a brief introduction section to your project, format the document with markdown syntax as you deem appropriate, and structure the analysis as you deem appropriate. Remember, marks will be awarded for completion of the 4 tasks, but 10 points of the whole project are allocated to a reproducible and clean analysis. If you feel lost, you can find a sample data analysis [here](https://www.kaggle.com/headsortails/tidy-titarnic) to have a better idea. However, bear in mind that it is **just an example** and you will not be required to have that level of complexity in your project.

#Final choice: **Cancer sample**

# Task 2: Exploring your dataset (15 points)

##About the data set 
The cancer sample data set was obtained from the UCI Machine Learning Repository. This data explores the characteristics of cell nuclei taken from breast tissue to scan for cancer. The samples were collected using a fine needle aspirate technique and the data presented on the table was processed through artificial intelligence. Some of the information contained in the data set is:

1: ID of the patient
2: Diagnosis (B=benign or M=malign)
3: radius
4: texture
5: perimeter
6: area
7: smoothness
8: compactness
9: concavity
10: concave points
11: symmetry
12: fractal dimension

It is also important to take into account that the data collected from these variable are mean, standard error(se) and worst (largest).

## About the tools
In order to explore the data set, we will be using the ggplot2 and dplyr packages. The first one is used to generate different graph types (boxplot, scatter plot, histogram, barplot, etc) on R studio, while the second one is focused on manipulation of the data such as adding, selecting, filetering and reducing variables. When creating graphs with ggplot, the tibble is always the first argument followed by aesthetic mapping; layers can be added using geom functions.

If we rewind and go back to the learning objectives, you'll see that by the end of this deliverable, you should have formulated *4* research questions about your data that you may want to answer during your project. However, it may be handy to do some more exploration on your dataset of choice before creating these questions - by looking at the data, you may get more ideas. **Before you start this task, read all instructions carefully until you reach START HERE under Task 3**.

2.1 Complete *4 out of the following 8 exercises* to dive deeper into your data. All datasets are different and therefore, not all of these tasks may make sense for your data - which is why you should only answer *4*. Use *dplyr* and *ggplot*.

1.  Plot the distribution of a numeric variable.
2.  Create a new variable based on other variables in your data (only if it makes sense)
3.  Investigate how many missing values there are per variable. Can you find a way to plot this?
4.  Explore the relationship between 2 variables in a plot.
5.  Filter observations in your data according to your own criteria. Think of what you'd like to explore - again, if this was the `titanic` dataset, I may want to narrow my search down to passengers born in a particular year...
6.  Use a boxplot to look at the frequency of different observations within a single variable. You can do this for more than one variable if you wish!
7.  Make a new tibble with a subset of your data, with variables and observations that you are interested in exploring.
8.  Use a density plot to explore any of your variables (that are suitable for this type of plot).

2.2 For each of the 4 exercises that you complete, provide a *brief explanation* of why you chose that exercise in relation to your data (in other words, why does it make sense to do that?), and sufficient comments for a reader to understand your reasoning and code.


## Part 2.1
### Exercise 1:
To explore the cancer data set focusing on the symmetry and area mean, I created a scatter plot that explored the relationship of the two variables. It was very interesting to see that benign tumour samples cluster more closely than malign ones which hints into their cancer variability characteristics. 
<!-------------------------- Start your work below ---------------------------->
```{r}
### 1) Explore the relationship between 2 variables in a plot.
symarea<-ggplot(cancer_sample,aes(symmetry_mean,area_mean))+
  geom_point(mapping=aes(fill=diagnosis),shape=21)+
  labs(y="Area Mean",x="Symmetry Mean",title="Relationship between area and symmetry mean")+
  theme(plot.title = element_text(hjust = 0.5))
symarea
```

### Exercise 2:
I utilized the boxplot graph to look at the observation of mean area for both benign and malign tumors. This graph showed a similar pattern as the last one where malign tumors show more variability. For this reason, it was important to separate both groups when doing the boxplot  as they behave differently and they could mask each other is nalyzed together. 
```{r}
### 2) Use a boxplot to look at the frequency of different observations within a single variable. You can do this for more than one variable if you wish!
areadis<-ggplot(cancer_sample, aes(diagnosis,area_mean))+
  geom_boxplot(color="purple",alpha=0.6,width=0.3)+
  labs(y="Mean area of cell nuclei in biopsy",title="Mean area of cell nuclei in biopsy")+
  theme(plot.title = element_text(hjust = 0.5))
areadis
```
### Exercise 3:
Sometimes it is easier to classify numerical values into categories that will be clearer about the significance of the value obtained. This was the case when analyzing the area standard error which I was hoping would give me an insight into the variability of each area measurement.Therefore I classified the area_se as high or low depending on their value (higher or lower than 50 which I found was around the mean of the mean area).
```{r}
### 3) Create a new variable based on other variables in your data (only if it makes sense)
cancer_sample%>%
  select(ID, diagnosis, area_mean, area_se)%>%
  mutate(area_variability=case_when(area_se>50~'high',
                                      area_se<50~'low'))
```
`### Exercise 4:
The **density plot** was done with the data of the area_mean variable. It was helpful to visualize the distribution of the data. The benign tumors seem to behave in a consistent pattern in regards to their mean area. 
````{r}
### 4) Use a density plot to explore any of your variables (that are suitable for this type of plot).
area_density<-ggplot(cancer_sample,aes(area_mean))+
  geom_density(aes(fill=diagnosis),alpha=0.3)+
  labs(y="Density",x="Area mean",title="Density plot of nuclei mean area")+
  theme(plot.title = element_text(hjust = 0.5))
area_density
```
<!----------------------------------------------------------------------------->

# Task 3: Write your research questions (5 points)

**So far, you have chosen a dataset and gotten familiar with it through exploring the data. Now it's time to figure out 4 research questions that you would like to answer with your data! Write the 4 questions and any additional comments at the end of this deliverable. These questions are not necessarily set in stone - TAs will review them and give you feedback; therefore, you may choose to pursue them as they are for the rest of the project, or make modifications!**

<!--- *****START HERE***** --->
1.Do malign tumors have a higher standard error (in terms of area) than benign tumors?
2.Is symmetry correlated to an increased nuclei area in malign tumors?
3. Is symmetry related to the diagnosis of a patient?
4. Is concavity correlated to the perimeter of the nuclei?

# Task 4: Process and summarize your data (13 points)

**From Task 2, you should have an idea of the basic structure of your dataset (e.g. number of rows and columns, class types, etc.). Here, we will start investigating your data more in-depth using various data manipulation functions.**

### 1.1 (10 points)

**Now, for each of your four research questions, choose one task from options 1-4 (summarizing), and one other task from 4-8 (graphing). You should have 2 tasks done for each research question (8 total). Make sure it makes sense to do them! (e.g. don't use a numerical variables for a task that needs a categorical variable.). Comment on why each task helps (or doesn't!) answer the corresponding research question.**


**Summarizing:**

1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.
2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!
3.  Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior".*
4.  Based on two categorical variables, calculate two summary statistics of your choosing.

**Graphing:**

5.  Create a graph out of summarized variables that has at least two geom layers.
6.  Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.
7.  Make a graph where it makes sense to customize the alpha transparency.
8.  Create 3 histograms out of summarized variables, with each histogram having different sized bins. Pick the "best" one and explain why it is the best.

Make sure it's clear what research question you are doing each operation for!

<!------------------------- Start your work below ----------------------------->
```{r}
#1)Do malign tumors have a higher standard error (in terms of area) than benign tumors?
#Summarizing: (1) Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.
#
sum_stat_conc <- cancer_sample %>%
  group_by(diagnosis) %>%
  arrange(area_se)  %>%
  summarise(Mean_area_se = mean(area_se),
            SD_srea_se = sd(area_se),
            Min_area_se = min(area_se),
            Median_area_se = median(area_se),
            Max_area_se = max(area_se), n=n()) %>%
  mutate(across(where(is.numeric), ~ round(., 1)))
sum_stat_conc

#Graphing: (5) Create a graph out of summarized variables that has at least two geom layers.
area_se_diag<-ggplot(cancer_sample,aes(diagnosis,area_se))+
  labs(title="Standard error of nuclei area in breast cancer tumors", y ="Standard error area", x = "Diagnosis", )+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_boxplot(aes(fill=diagnosis), alpha=0.5)+
  geom_text(data = sum_stat_conc, aes(y=Mean_area_se, label = round(Mean_area_se,2)), hjust=0) 

area_se_diag
```

```{r}
#3) Are symmetry and area related to the diagnosis of a patient?
#Summarizing: (3) Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks!

###I ran the statistical summary of area_mean and symmetry_mean to be able to define the categories for the new variable (anything higher than the mean, is consider "increased")
sum_stat_conc1 <- cancer_sample %>%
  group_by(diagnosis) %>%
  arrange(area_mean)  %>%
  summarise(Mean_area_mean = mean(area_mean),
            SD_area_mean = sd(area_mean),
            Min_area_mean = min(area_mean),
            Median_area_mean = median(area_mean),
            Max_area_mean = max(area_mean), n=n()) %>%
  mutate(across(where(is.numeric), ~ round(., 1)))
sum_stat_conc1

sum_stat_conc2 <- cancer_sample %>%
  group_by(diagnosis) %>%
  arrange(symmetry_mean)  %>%
  summarise(Mean_symmetry_mean = mean(symmetry_mean),
            SD_symmetry_mean = sd(symmetry_mean),
            Min_symmetry_mean = min(symmetry_mean),
            Median_symmetry_mean = median(symmetry_mean),
            Max_symmetry_mean = max(symmetry_mean), n=n()) %>%
  mutate(across(where(is.numeric), ~ round(., 1)))
sum_stat_conc2


cancer_sample%>%
  select(ID, diagnosis, area_mean, symmetry_mean)%>%
  mutate(sym_area_pattern=case_when(area_mean>460 & symmetry_mean<0.2 ~'increased area only',
                                      area_mean<460 & symmetry_mean>0.2~'increased symmetry only',
                                    area_mean>460 & symmetry_mean>0.2~'increased symmetry and area'))

#Graphing: (7) Make a graph where it makes sense to customize the alpha transparency.
symmetry_density<-ggplot(cancer_sample,aes(symmetry_mean))+
  geom_density(aes(fill=diagnosis),alpha=0.3)+
  labs(y="Density",x="Symmetry mean",title="Density plot of nuclei mean symmetry")+
  theme(plot.title = element_text(hjust = 0.5))
symmetry_density


```
```{r}
#1)Is symmetry correlated to an increased nuclei area in malign tumors?
#Summarizing: (2) Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!
sym_M <- cancer_sample %>%
  rename(c("symmetry"="symmetry_mean", "area"="area_mean")) %>%
  select(diagnosis, symmetry, area) %>%
  arrange(symmetry)%>%
  filter(diagnosis == "M")
sym_M

sym_M_count <- count(sym_M, diagnosis)
head(sym_M_count)

#Graphing: (8) Create 3 histograms out of summarized variables, with each histogram having different sized bins. Pick the "best" one and explain why it is the best.
Hist_1 <- ggplot(cancer_sample, aes(x=symmetry_mean)) + 
  geom_histogram(aes(fill=diagnosis), alpha = 0.3, binwidth=0.05) +
  ggtitle("Symmetry mean with bin size = 0.05")
Hist_1

Hist_2 <- ggplot(cancer_sample, aes(x=symmetry_mean)) + 
  geom_histogram(aes(fill=diagnosis), alpha = 0.3, binwidth=0.005) +
  ggtitle("Symmetry mean with bin size = 0.005")
Hist_2

Hist_3 <- ggplot(cancer_sample, aes(x=symmetry_mean)) + 
  geom_histogram(aes(fill=diagnosis), alpha = 0.3, binwidth=0.0005) +
  ggtitle("Symmetry mean with bin size = 0.0005")
Hist_3


```

```{r}
#1)Is concavity correlated to the diagnosis of the patient?
#Summarizing: (4) Based on two categorical variables, calculate two summary statistics of your choosing.

#Categorical variable 1: Diagnosis
###By turning the categorical variable into a numeric one, we can calculate the mean, standard deviation, minimum value, median and maximum value.
diagnosis_num_stat <- cancer_sample %>%
    mutate(diagnosis_num=case_when(diagnosis=="M" ~1,
                                  diagnosis=="B" ~0 ))%>%
  arrange(diagnosis_num)  %>%
  summarise(Mean_diagnosis_num = mean(diagnosis_num),
            SD_diagnosis_num = sd(diagnosis_num),
            Min_diagnosis_num = min(diagnosis_num),
            Median_diagnosis_num = median(diagnosis_num),
            Max_diagnosis_num = max(diagnosis_num), n=n()) %>%
  mutate(across(where(is.numeric), ~ round(., 1)))
diagnosis_num_stat

###Frequency table
cancer_sample%>%
  count(diagnosis, sort=TRUE)

###Calculating percentage 
cancer_sample %>%
     group_by(diagnosis)%>%
     summarise(percent=100*n()/nrow(cancer_sample))


#Categorical variable 2: area variability
#As there is no other categorical value in the data set that would serve for summary statistics, I converted the....

###By turning the categorical variable into a numeric one, we can calculate the mean, standard deviation, minimum value, median and maximum value.
areavar_stat<-cancer_sample %>%
    select(ID, diagnosis, area_mean, area_se)%>%
    mutate(area_variability=case_when(area_se>50~'high',
                                      area_se<50~'low'))%>%
  mutate(areavar_num=case_when(area_variability=="high" ~1,
                                  area_variability=="low" ~0 ))%>%
  arrange(areavar_num)  %>%
  summarise(Mean_areavar = mean(areavar_num),
            SD_areavar = sd(areavar_num),
            Min_areavar = min(areavar_num),
            Median_areavar = median(areavar_num),
            Max_areavar = max(areavar_num), n=n()) %>%
  mutate(across(where(is.numeric), ~ round(., 1)))
areavar_stat

###Frequency table
cancer_sample%>%
  select(ID, diagnosis, area_mean, area_se)%>%
  mutate(area_variability=case_when(area_se>50~'high',
                                      area_se<50~'low'))%>%
  count(area_variability, sort=TRUE)

###Calculating percentage 
cancer_sample %>%
    select(ID, diagnosis, area_mean, area_se)%>%
    mutate(area_variability=case_when(area_se>50~'high',
                                      area_se<50~'low'))%>%
    group_by(area_variability)%>%
    summarise(percent=100*n()/nrow(cancer_sample))


#Graphing: (6) Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.

conc_log10 <- ggplot(cancer_sample, aes(concavity_mean, area_mean)) + 
  geom_point() +
  geom_smooth(method = lm, formula = y ~ x) +
  scale_y_continuous(trans = log10_trans(),
    breaks = trans_breaks("log10", function(x) 10^x),
    labels = trans_format("log10", math_format(10^.x))) +
    labs(title="Concavity vs Area of the nuclei in malignant breast tumors", y ="Concavitys", x = "Area")
print(conc_log10)
```
<!----------------------------------------------------------------------------->

### 1.2 (3 points)

**Based on the operations that you've completed, how much closer are you to answering your research questions? Think about what aspects of your research questions remain unclear. Can your research questions be refined, now that you've investigated your data a bit more? Which research questions are yielding interesting results?**

<!-------------------------- Start your work below ---------------------------->
Questions: 1.Do malign tumors have a higher standard error (in terms of area) than benign tumors?
2.Is symmetry correlated to an increased nuclei area in malign tumors?
3. Is symmetry related to the diagnosis of a patient?
4. Is concavity correlated to the perimeter of the nuclei?

In the last task I deviated from some of my original questions to follow the list of activities proposed. The first question was answered well with both the summarizing an graphing methods.As for the second, I deviated from the original question to be able to create a new variable which is related to the question but does not offer a definitive answer. I think this could be further worked on by making the categorization more strict and defined as I just took the mean and defined anything above as "increased", but maybe a better approach is to take the quantile data or do more literature research on normal parameters. The same happens with the third question where I investigate the relation between symmetry and diagnosis of the patient. This serves as an broad overview to the answer of the question but it is lacking in analysis to correlation. Lastly, on the last question I changed my concavity variable for the area_se as I found it easier to work on with and the parameters to make it a categorical value had been previously defined.

<!----------------------------------------------------------------------------->

### Attribution

Thanks to Icíar Fernández Boyano for mostly putting this together, and Vincenzo Coia for launching.
